---
title: "Persistent Player Profiles"
author: "Anthony Pileggi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
Player information is stored in a local file.  By default, this file is call `.casino`
and it is placed in the current working directory.

```{r}
library(casino)

# create a new file to store player profiles
setup()

# create some players
Player$new("Player 1")

# check the available players
players()
```


# Multiple Players
You can store multiple players in the same profile file.

```{r}
# create more players
Player$new("Player 2")
Player$new("Player 3")

# check the available players
players()
```


# Multiple Profile Files
If you want to store multiple player profiles, you can specify the filename.

```{r}
# first profile
setup(".bellagio")
Player$new("Player 1")
Player$new("Player 2")
players()

# second profile
setup(".caesars")
Player$new("Player 3")
Player$new("Player 4")
players()

# now switch back to the first one
setup(".bellagio")
players()
```


# Delete Profiles
If you want to delete all players in the current profile and reset the `casino` package, use the `delete()` function.

```{r}
# delete current profile (.bellagio)
delete()

# delete a different profile (.caesars)
setup(".caesars")
delete()

# delete the default profile (.casino)
setup()
delete()
```